Replication of Gantman et al. 2024

### 2024-04-01 manuscript.qmd
fix error in GEE model

eeg_data_key_corrected_study_1 <- eeg_data_study_1 %>%
  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
  mutate(correct = ifelse(subject == "36" & word_type == "moral", !correct, correct))
```

@@

time_window_data_study_1 <- eeg_data_study_1 %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  mutate(erp_component = get_time_window(t)) %>%
  filter(erp_component != "other") %>%
  group_by(subject, electrode, word_type, is_word, erp_component) %>%
  summarize(v = mean(v)) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

@@

In the moral condition, there were no significant differences between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`).

@@

In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`). There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).

>>>>

eeg_data_key_corrected_study_1 <- eeg_data_study_1 %>%
  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
  mutate(correct = ifelse(subject == "36" & (word_type == "moral" | word_type == "non-moral"), !correct, correct))
```

@@

time_window_data_study_1 <- eeg_data_key_corrected_study_1 %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  mutate(erp_component = get_time_window(t)) %>%
  filter(erp_component != "other") %>%
  group_by(subject, event_id, electrode, word_type, is_word, erp_component) %>%
  summarize(v = mean(v)) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

@@

In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), but this difference was in the opposite direction predicted by Gantman et al. (2020). There were no significant differences between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`).

@@

In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`) and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`). There was no significant difference in the P2 window ($\beta$ = `r p2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`) and N2 window ($\beta$ = `r n2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
